Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-05-05 paper.tex
Remove reference to deleted figure
Remove a line

A process may use the \texttt{mmap} system call to request that the kernel
allocate part of its virtual address space. Accesses to memory addresses
outside of allocated regions result in a segmentation fault.
The Linux kernel keeps track of which portions of a process's address space
have been allocated using the \texttt{vm\_area\_struct} data structure. Because
processes may map a number of regions, including shared objects, stack, heap,
text, and anonymous regions, the scalability of this structure is critical to
Linux's performance.

@@

Under memory pressure, the kernel may choose to write some pages of memory to
disk and then free those pages for use. Memory mapped files are written back to
their backing files, but anonymous memory is written to portion of the disk
called swap space. We focus on anonymous memory in our experiments.

@@

The \texttt{cont} benchmark has more surprising results. Notice that Figure
\ref{fig:swap_time_cont} has a logarithmic y-scale. The system only begins to
swap after about 4M operations, as before. Unlike the \texttt{rand} benchmark, we see a
number of operations that take hundreds of milliseconds. Figure
\ref{fig:swap_time_cont_cdf} shows that these only form a fraction of a percent
of all accesses done after swapping starts. However, Figure
\ref{fig:swap_time_cdf} shows that these few accesses form a majority of run
time; they impact performance significantly.

>>>>

A process may use the \texttt{mmap} system call to request that the kernel
allocate part of its virtual address space.
The Linux kernel keeps track of which portions of a process's address space
have been allocated using the \texttt{vm\_area\_struct} data structure. Because
processes may map a number of regions, including shared objects, stack, heap,
text, and anonymous regions, the scalability of this structure is critical to
Linux's performance.

@@

Under memory pressure, the kernel may free some pages for use by writing some
pages to disk. Memory mapped files are written back to their backing files,
but anonymous memory is written to portion of the disk called swap space. We
focus on anonymous memory in our experiments.

@@

The \texttt{cont} benchmark has more surprising results.
The system only begins to
swap after about 4M operations, as before. Unlike the \texttt{rand} benchmark, we see a
number of operations that take hundreds of milliseconds. Figure
\ref{fig:swap_time_cont_cdf} shows that these only form a fraction of a percent
of all accesses done after swapping starts. However, Figure
\ref{fig:swap_time_cdf} shows that these few accesses form a majority of run
time; they impact performance significantly.
